---
title: "Final Project"
author: "Jiawei Li"
date: "2017/12/18"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, include=FALSE}
library(knitr)
library(tm)
library(kableExtra)
library(devtools)
library(twitteR)
library(dplyr)
library(stringr)
library(tidytext)
library(ggplot2)
library(RColorBrewer)
library(wordcloud)
library(ggmap)
```



```{r, eval=FALSE, include=FALSE}
#twitter setup 
api_key <- 	"eObfQ5EtrT0ryjSTrPFoGC7kM"
api_secret <- "asm7zEQwiiWB9DZzYeUfUSB8gUeJzknCnLvD1sVzdaDmlJlcSQ"
access_token <- "938520753326247937-s5l1XCbZ4LFCdSGB7syLXpT50xR91br"
access_token_secret <- "C8aHFFL8JCZwWUSyb7CQGOt5hkEKxotlOGJcTsVGiKNZu"

setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)
a11 <- searchTwitter("#Rihanna+#rihanna",n=5000)
a12 <-twListToDF(a11)
write.csv(a12,file = "Rihanna.csv",row.names=TRUE)
aT1 <- searchTwitter("#TaylorSwift+#taylorswift",n=5000)
aT2 <-twListToDF(aT1)
write.csv(aT2,file = "TS.csv",row.names=TRUE)

```

#Text analysis  

Topic #Rihanna 


Topic #Taylor Swift

##Search Topic

First search 5000 results of the topic #Rihanna from Twitter.


It looks like most of the data points I collected are in the area of Europe and United States.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

a10<- read.csv("Rihanna.csv",header = T)
a13 <- -1*is.na(a10$longitude)+1
sum(a13)
a14 <- which(a13==1)
locationa11 <-data.frame(a10$latitude[a14],a10$longitude[a14])
colnames(locationa11) <- c("latitude","longitude")
locationa11$longitude<-as.numeric(locationa11$longitude)
locationa11$latitude <-as.numeric(locationa11$latitude)  
map.world <- map_data(map = "world")
ggplot() + geom_polygon(data = map.world, aes(x=long, y = lat, group = group),fill="rosybrown",color="rosybrown") + 
  coord_fixed(1.3)+geom_point(data= locationa11,
                              aes(x = longitude, y = latitude),
                              colour = "salmon",
                              alpha = 0.5,
                              size = 0.5)+ggtitle("The Map of the Data Points-Rihanna")

```



##Calculate the count of tweets by platform.

Here is the barplot of the count of the source
Most of the tweets are from Android, and then is Iphone.

```{r, echo=FALSE, message=FALSE, warning=FALSE}



a10_platform <- a10 %>% group_by(statusSource) %>% 
  summarize(n = n()) %>%
  mutate(percent_of_tweets = n/sum(n)) %>% arrange(desc(n))
a10_platform$percent_of_tweets <- round(a10_platform$percent_of_tweets, digits = 3)
a10_plat_5 <- a10_platform %>% top_n(5)
kable(a10_plat_5)



ggplot(a10_plat_5,aes(statusSource,y=n))+geom_bar(stat = "identity",width = 0.5,fill="lightpink")+
  coord_flip()+geom_text(aes(label=n),vjust=-.3,size=3.5)+
  theme_minimal()+ggtitle("The Counts of the Data From Different Platform-Rihanna")

```



```{r, message=FALSE, warning=FALSE, include=FALSE}


replace_reg <- "https://t.co/[A-Za-z\\d]+|http://[A-Za-z\\d]+|&amp;|&lt;|&gt;|RT|https"
unnest_reg <- "([^A-Za-z_\\d#@']|'(?![A-Za-z_\\d#@]))"
a15 <- a10 %>% 
  filter(!str_detect(text, "^RT")) %>%
  mutate(text = str_replace_all(text, replace_reg, "")) %>%
  unnest_tokens(word, text, token = "regex", pattern = unnest_reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

nrc <- sentiments %>%
  filter(lexicon == "nrc") %>%
  select(word, sentiment)
```



##Sentiment of total data

After clean the data, plot the Sentiment of Topic #Rihanna in total.
We can see that most of the words are positive in the topic of #Rihanna. The least is disgust.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

a15_sentiment <- a15 %>% inner_join(nrc, by = "word")
a15_sent <- a15_sentiment %>% group_by(sentiment) %>% summarize(n = n()) %>% arrange(desc(n))

ggplot(a15_sent,aes(sentiment,y=n))+geom_bar(stat = "identity",fill="lightpink1")+geom_text(aes(label=n))+
  theme_minimal()+ggtitle("The Plot of Sentiment words--Total(Rihanna)")

a16_words <- a15 %>% group_by(word) %>% summarize(n = n()) %>% arrange(desc(n)) %>% top_n(10)


```

##Sentiment of top 5 data source

Calculate and plot the Sentiment of Topic #Rihanna from different data source platform.
By comparing the sentiment from different data platforms, we can see that positive and joy words have biggest part in the bar.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

DS <- c("Twitter for iPhone","Twitter for Android","Twitter Web Client","TweetDeck","Twitter Lite")
a15_Source0 <- a15 %>% filter(statusSource %in% DS)
a15_Source <- a15_Source0 %>%
  group_by(statusSource) %>%
  mutate(total_words = n()) %>%
  ungroup() %>%
  distinct(id, statusSource, total_words)

a15_Source5 <- a15_Source0 %>%
  inner_join(nrc, by = "word") %>%
  count(sentiment, id) %>%
  ungroup() %>%
  tidyr::complete(sentiment, id, fill = list(n = 0)) %>%
  inner_join(a15_Source) %>%
  group_by(statusSource, sentiment, total_words) %>%
  summarize(words = sum(n)) %>%
  ungroup()

a16_Source <- a15_Source5 %>% group_by(statusSource) %>% mutate(tot_sentiment = sum(words))

a16_Source <- a16_Source %>% mutate(percent_of_tweets = (words / tot_sentiment) * 100)
a16_Source$percent_of_tweets <- round(a16_Source$percent_of_tweets, digits = 2)


a17 <- a16_Source %>% select(statusSource, sentiment, percent_of_tweets)

ggplot(a17, aes(x=statusSource, y=percent_of_tweets, fill = sentiment)) + 
        geom_bar(stat = "identity", position = "stack",width = 0.5) +
        scale_fill_brewer(palette = "RdBu") + xlab("Data Source Platform--Rihanna") +
        ylab("Percent of Tweets") + theme(axis.text.x =element_text(angle = 60,hjust = 1))+
        ggtitle("Sentiment of Different Source of Tweets")


```

##Wordclouds Analysis--Top 10 words in the Topic(#Rihanna)

Plot the word coulds of #Rihanna.
Top 1 word is rihanna, which is obviously. But it is suprise that the secon word is bieber. We can also see that fentybeauty---the cosmetics brand establised by Rihanna herself is also in top 10.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
str(a15$word) 
a15word <- as.character(a15$word)
a15text <- Corpus(VectorSource(a15word))
a15text <- a15text %>%
  tm_map(removePunctuation)%>% 
  tm_map(removeNumbers)%>% 
  tm_map(stripWhitespace)%>%
  tm_map(tolower)%>% 
  tm_map(removeWords, stopwords("english"))

a15text <- tm_map(a15text,stemDocument)
a15count <- as.matrix(TermDocumentMatrix(a15text))
a15fre <- sort(rowSums(a15count),decreasing = T)
a15fd <- data.frame(word=names(a15fre),freq=a15fre)
ggplot(a15fd[1:10,],aes(x=reorder(factor(word), -freq),y=freq))+geom_bar(stat="identity",aes(fill=factor(word)))+
          theme(axis.text.x = element_text(angle = 60, hjust = 1))+ggtitle("Top 10--Rihanna")+
          xlab("Top10 Words") +
          ylab("Frequency")

```


##The Word clouds

Here is the word clouds of the topic #Rihanna.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(200)
wordcloud(words = names(a15fre),freq = a15fre,max.words=100, min.freq =2,scale=c(6, .6), 
          random.order=FALSE, rot.per=0.35,random.color = F, 
          colors= c("violetred","slateblue1","tomato"))
```




#Analysis of Taylor Swift




##Search Topic

First search 5000 results of the topic #Taylor Swift from Twitter.
It looks like most of the majority part of points I collected are in the United States. There is no points in the Africa.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
aT0 <-read.csv("TS.csv",header = T)
aT3 <- -1*is.na(aT0$longitude)+1
sum(aT3)
aT4 <- which(aT3==1)
locationaT1 <-data.frame(aT0$latitude[aT4],aT0$longitude[aT4])
colnames(locationaT1) <- c("latitude","longitude")
locationaT1$longitude<-as.numeric(locationaT1$longitude)
locationaT1$latitude <-as.numeric(locationaT1$latitude)  
map.world <- map_data(map = "world")
ggplot() + geom_polygon(data = map.world, aes(x=long, y = lat, group = group),color="slategray",fill="slategray") + 
  coord_fixed(1.3)+geom_point(data= locationaT1,
                              aes(x = longitude, y = latitude),
                              colour = "sienna1",
                              alpha = 0.5,
                              size = 0.5)
```


##Calculate the count of tweets by platform.

Here is the table of the count of the source.
Different from #Rihanna, most of the tweets contain topic #Taylor Swift are sent from IPhone.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

aT0_platform <- aT0 %>% group_by(statusSource) %>% 
  summarize(n = n()) %>%
  mutate(percent_of_tweets = n/sum(n)) %>% arrange(desc(n))
aT0_platform$percent_of_tweets <- round(aT0_platform$percent_of_tweets, digits = 3)
aT0_plat_5 <- aT0_platform %>% top_n(5)
kable(aT0_plat_5)
```

##Barplot of the count of the source

Here is the barplot of the count of the source.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

ggplot(aT0_plat_5,aes(statusSource,y=n))+geom_bar(stat = "identity",width = 0.5,fill="khaki")+
  coord_flip()+geom_text(aes(label=n),vjust=-.3,size=3.5)+
  theme_minimal()+
  ggtitle("The Counts of the Data From Different Platform-TS")


replace_reg <- "https://t.co/[A-Za-z\\d]+|http://[A-Za-z\\d]+|&amp;|&lt;|&gt;|RT|https"
unnest_reg <- "([^A-Za-z_\\d#@']|'(?![A-Za-z_\\d#@]))"
aT5 <- aT0 %>% 
  filter(!str_detect(text, "^RT")) %>%
  mutate(text = str_replace_all(text, replace_reg, "")) %>%
  unnest_tokens(word, text, token = "regex", pattern = unnest_reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

nrc <- sentiments %>%
  filter(lexicon == "nrc") %>%
  select(word, sentiment)
```

##Sentiment of total

After clean the data, plot the Sentiment of Topic #Taylor Swift in total.
The result below shows that positive words appear frequently in the topic of Taylor Swift.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Sentiment of total
aT5_sentiment <- aT5 %>% inner_join(nrc, by = "word")
aT5_sent <- aT5_sentiment %>% group_by(sentiment) %>% summarize(n = n()) %>% arrange(desc(n))

ggplot(aT5_sent,aes(sentiment,y=n))+geom_bar(stat = "identity",fill="khaki1")+geom_text(aes(label=n))+
  theme_minimal()+coord_flip()+ggtitle("The Plot of Sentiment words--Total(TS)")

aT6_words <- aT5 %>% group_by(word) %>% summarize(n = n()) %>% arrange(desc(n)) %>% top_n(10)
```


##Sentiment of top 5 data source

Calculate and plot the Sentiment of Topic #Taylor Swift from different data source platform.
The results is similar to the topic of #Rihanna.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#sentiment of top 5 data source

DS <- c("Twitter for iPhone","Twitter for Android","Twitter Web Client","TweetDeck","Twitter Lite")
aT5_Source0 <- aT5 %>% filter(statusSource %in% DS)
aT5_Source <- aT5_Source0 %>%
  group_by(statusSource) %>%
  mutate(total_words = n()) %>%
  ungroup() %>%
  distinct(id, statusSource, total_words)


aT5_Source5 <- aT5_Source0 %>%
  inner_join(nrc, by = "word") %>%
  count(sentiment, id) %>%
  ungroup() %>%
  tidyr::complete(sentiment, id, fill = list(n = 0)) %>%
  inner_join(aT5_Source) %>%
  group_by(statusSource, sentiment, total_words) %>%
  summarize(words = sum(n)) %>%
  ungroup()

aT6_Source <- aT5_Source5 %>% group_by(statusSource) %>% mutate(tot_sentiment = sum(words))

aT6_Source <- aT6_Source %>% mutate(percent_of_tweets = (words / tot_sentiment) * 100)
aT6_Source$percent_of_tweets <- round(aT6_Source$percent_of_tweets, digits = 2)


aT7 <- aT6_Source %>% select(statusSource, sentiment, percent_of_tweets)

ggplot(aT7, aes(x=statusSource, y=percent_of_tweets, fill = sentiment)) + 
  geom_bar(stat = "identity", position = "stack",width = 0.5) +
  scale_fill_brewer(palette = "RdBu") + xlab("Data Source Platform--TS") +
  ylab("Percent of Tweets") + theme(axis.text.x =element_text(angle = 60,hjust = 1))+
  ggtitle("Sentiment of Different Source of Tweets")

```

##Wordclouds Analysis--Top 10 words in the Topic(#Taylor Swift)

The character of "Taylor Swift" appears a lot in the top 10 words.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

str(aT5$word) 
aT5word <- as.character(aT5$word)
aT5text <- Corpus(VectorSource(aT5word))
aT5text <- aT5text %>%
  tm_map(removePunctuation)%>% 
  tm_map(removeNumbers)%>% 
  tm_map(stripWhitespace)%>%
  tm_map(tolower)%>% 
  tm_map(removeWords, stopwords("english"))

aT5text <- tm_map(aT5text,stemDocument)
aT5count <- as.matrix(TermDocumentMatrix(aT5text))
aT5fre <- sort(rowSums(aT5count),decreasing = T)
aT5fd <- data.frame(word=names(aT5fre),freq=aT5fre)
ggplot(aT5fd[1:10,],aes(x=reorder(factor(word), -freq),y=freq))+geom_bar(stat="identity",aes(fill=factor(word)))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

##The Word Clouds

Here is the word clouds of topic #Taylor Swift.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(200)
wordcloud(words = names(aT5fre),freq = aT5fre,max.words=200, min.freq =2,scale=c(6, .6), 
          random.order=FALSE, rot.per=0.35,random.color = F, 
          colors= c("royalblue1","palegreen1","violetred3"))

```

